detect patches

### 2024-02-15 scripts/classify_patches.Rmd
blm ownership simplified
working towards splitting data for crews

}
lapply(f, tif2shp)

@@

>>>>

@@

detect neighboring patches

```{r detect neighboring patches up to 5 orders, eval = F}

f <- list.files('../results/allOccupiedPatchesVector', pattern = 'shp$')

lapply(f, neigh_type)

These previous patches refer to pre-Colombian connectivity. We will reduce them to BLM surface areas.

```{r crop patches to BLM, eval = F}
blm_admin_surf <- st_read('/media/steppe/hdd/Geospatial_data/Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp') %>% 
  select(geometry)
f <- paste0('../results/rankedPatches/', list.files('../results/rankedPatches/', pattern = '.shp$'))

crop2blm <- function(x){

  taxon <- gsub('.shp$', '', basename(x))
  patches <- sf::st_read(x, quiet = TRUE) |> 
    sf::st_make_valid()
  blm_patches <- sf::st_intersection(patches, blm_admin_surf)
  blm_patches <- sf::st_make_valid(blm_patches) |>
    sf::st_collection_extract(type = c("POLYGON"))

  blm_patches <- blm_patches[!sf::st_is_empty(blm_patches),]
  sf::st_write(blm_patches, paste0('../results/PatchesClippedBLM/', taxon, '.shp'), quiet = TRUE)
}

lapply(f, crop2blm)
```
